An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2020-05-22 gas-adsorption/gas-ads.tex
remove out of date comments and answer comments.
working through the paper and making edits and removing outdated comments.
use bold face for all vectors
made cory comment fixes for abstract.

% \usepackage{cite}
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
\usepackage{color}  % Coloured text etc.
%
\usepackage[colorinlistoftodos,prependcaption,textsize=normalsize]{todonotes}
\usepackage{mdframed}

\newcommand{\addcite}{{\bf \color{red} []}}
\newcommand{\xvec}{\mathbf{x}}
\newcommand{\thetavec}{\boldsymbol \theta}

\newcommand\V{\Phi}
\newcommand\Vk{\tilde\Phi(\vec k)}
\newcommand\volume{V}

@@

%\newcommandx{\davidsays}[1]{\begin{mdframed}[backgroundcolor=blue!24]\textbf{David says:} #1\end{mdframed} }
%\newcommandx{\davidsays}[2][1=inline]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{\textbf{David says:} #2} }
\newcommand{\davidsays}[1]{{\color{red} [\blue{D:} \emph{#1}]}}
\newcommand{\jpsays}[1]{{\color{red} [\blue{Jordan:} \emph{#1}]}}
\newcommandx{\jordan}[2][1=inline]{\todo[linecolor=gray,backgroundcolor=gray!25,bordercolor=gray,#1]{\textbf{Jordan says:} #2} }
\newcommandx{\corysays}[2][1=inline]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green,#1]{\textbf{Cory says:} #2} }

%% \renewcommand\davidsays[1]{}
%% \renewcommand{\corysays}[2][1=inline]{}
%TC:macro \corysays [ignore]
%TC:macro \davidsays [ignore]
%TC:macro \jordan [ignore]

@@

\begin{document}
\title{
An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials}
% other ideas:
%Gas delivery via pressure-swing adsorption in nanoporous materials: setting storage targets}
% A thermodynamic upper bound to gas delivery via pressure-swing adsorption in nanoporous materials:}

@@

\begin{abstract}
Due to their low volumetric energy density at ambient conditions, both hydrogen
and natural gas are challenging to economically store onboard environmentally
sustainable vehicles~\cite{mason2014evaluating, sircar2002pressure}. One
strategy to densify these gases is to pack the fuel tank with a porous
material~\cite{?}. Metal-organic frameworks (MOFs) are tunable, nanoporous
materials with large internal surface areas and show considerable promise for
densifying gases~\cite{makal2012methane,mason2014evaluating,
suh2011hydrogen,garcia2018benchmark, schoedel2016role}. The US Department of
Energy (DOE) has set volumetric deliverable capacity targets~\cite{simon2015materials, h2targetsDOE} which, if met, would help to enable 
commercial adoption of hydrogen/natural gas as
transportation fuels. Many have attempted to establish theoretical upper bounds
on the deliverable capacity via pressure-swing adsorption using simplified
models of the gas-substrate and gas-gas interaction~\cite{gomez2014exploring, 
gomez2017impact, kaija2018high, lee2019predicting}; none have
established a rigorous upper bound on the deliverable capacity.
Here, we present a theoretical upper bound on the deliverable capacity of a
rigid material via an isothermal pressure-swing. To provide an extremum, we
consider a substrate that provides a spatially uniform potential energy field
for the gas. Our bound is unique in that it directly relies on experimentally
measured properties of the (real) bulk gas, without making approximations.
We conclude that the goals set by the US DOE for natural gas and hydrogen
storage are theoretically possible, but sufficiently close to the upper bound
as to be impractical for any real porous material. However, limitations to the
scope of applicability of our upper bound guide future material development 
efforts. Firstly, one could heat the adsorbent to drive off residual gas when
the pressure diminishes~\cite{gomez2014exploring}. Secondly, the fundamental
physics of our upper bound do not pertain to any material that changes its
structure in response to adsorbed gas, suggesting that flexible materials could
still satisfy the DOE targets~\cite{schneemann2014flexible, choi2008broadly, mason2015methane}.

%   Here, we present a theoretical upper bound on the deliverable capacity of a rigid material via an isothermal pressure-swing. % "pressure-swing storage doesn't make sense to me. storage and delivery  maybe but awk.
%   % I added rigid since that could be important...
%   To provide an extremum, we consider a substrate that provides a spatially uniform potential energy field for the gas. 
%   \davidsays{Maybe we can add a phrase for an optimal uniform attraction?}
%   Our bound is unique in that it directly relies on experimentally measured properties of the (real) bulk gas, without making approximations.
%   We conclude that the goals set by the US DOE for natural gas and hydrogen storage are theoretically possible, but sufficiently close to the upper bound as to be impractical for any real porous material.
%   % However, this upper bound directly leads to important realizations which should guide future development.
%   However, limitations to the scope of applicability of our upper bound guide future material development efforts.
%  % Firstly, one could extract the gas at a higher temperature than that used while filling [].
%   Firstly, one could heat the adsorbent to drive off residual gas when the pressure diminishes [].
%   Secondly, the fundamental physics of our upper bound do not pertain to
%   % rule out
%   any material that changes its structure in response to adsorbed gas, suggesting that flexible materials could still satisfy the DOE target [].
%   % firstly, secondly vs first, second?
\end{abstract}

@@

\paragraph*{to do}
\begin{enumerate}
    \item See david/corysays
    \item make the code presentable
    \item do the FIXME in code
\end{enumerate}

>>>>

% \usepackage{cite}
\usepackage{xargs}
% Use more than one optional parameter in a new commands
\usepackage{color}
%
\usepackage[colorinlistoftodos,prependcaption,textsize=normalsize]{todonotes}
\usepackage{mdframed}

\newcommand{\addcite}{{\bf \color{red} []}}
\newcommand{\rvec}{\mathbf{r}}
\newcommand{\kvec}{\mathbf{k}}
\newcommand{\thetavec}{\boldsymbol \theta}

\newcommand\V{\Phi}
\newcommand\Vk{\tilde\Phi(\kvec)}
\newcommand\volume{V}

@@

\newcommand{\davidsays}[1]{{\color{red} [\blue{D:} \emph{#1}]}}
\newcommand{\jpsays}[1]{{\color{red} [\blue{Jordan:} \emph{#1}]}}
\newcommandx{\jordan}[2][1=inline]{\todo[linecolor=gray,backgroundcolor=gray!25,bordercolor=gray,#1]{\textbf{Jordan says:} #2} }
\newcommandx{\corysays}[2][1=inline]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green,#1]{\textbf{Cory says:} #2} }

@@

\begin{document}
\title{
An upper bound to gas storage and delivery via pressure-swing adsorption in
porous materials}

@@

\begin{abstract}
Due to their low volumetric energy density at ambient conditions, both hydrogen
and natural gas are challenging to economically store onboard vehicles as
fuels~\cite{mason2014evaluating, sircar2002pressure}. One strategy to densify
these gases is to pack the fuel tank with a porous
material~\cite{schoedel2016role}. Metal-organic frameworks (MOFs) are tunable,
nanoporous materials with large internal surface areas and show considerable
promise for densifying gases~\cite{makal2012methane,mason2014evaluating,
suh2011hydrogen,garcia2018benchmark, schoedel2016role}. The US Department of
Energy (DOE) has set volumetric deliverable capacity
targets~\cite{simon2015materials, h2targetsDOE} which, if met, would help
enable commercial adoption of hydrogen/natural gas as transportation fuels.
Many have attempted to establish theoretical upper bounds on the deliverable
capacity via pressure-swing adsorption using simplified models of the
gas-substrate and gas-gas interaction~\cite{gomez2014exploring,
gomez2017impact, kaija2018high, lee2019predicting}; none have established a
rigorous upper bound on the deliverable capacity. Here, we present a
theoretical upper bound on the deliverable capacity of a rigid material via an
isothermal pressure-swing. To provide an extremum, we consider a substrate that
provides a spatially uniform potential energy field for the gas. Our bound is
unique in that it directly relies on experimentally measured properties of the
(real) bulk gas, without making approximations. We conclude that the goals set
by the US DOE for natural gas and hydrogen storage are theoretically possible,
but sufficiently close to the upper bound as to be impractical for any real
porous material. However, limitations to the scope of applicability of our
upper bound guide future material development efforts. Firstly, one could heat
the adsorbent to drive off residual gas trapped in the
adsorbent~\cite{gomez2014exploring}. Secondly, the fundamental physics of our
upper bound do not pertain to any material that changes its structure in
response to adsorbed gas, suggesting that flexible materials could still
satisfy the DOE targets~\cite{schneemann2014flexible, choi2008broadly,
mason2015methane}.

\end{abstract}

@@
